### 2021-06-20 docs/manuscript/manuscript.tex
Fix degree dist section

The degree distribution of this network seems to follow a Poisson distribution
(Pearson’s $\chi^2 = 12.8902$, $\text{p-value} = 0.115684$) characteristic of a
Erdös-Rényi network~\cite{Erdos1959}. This kind of network presents a great
number of nodes with low degree and a few nodes with high degree
(Fig~\ref{fig:deg-dist}A). Nodes corresponding to topologies number one and
three showed the highest degree ($deg(1) = deg (3) = 14$). Curiously, nodes with
higher degree resulted to be also those network topologies with higher abundance
(Fig~\ref{fig:deg-dist}B). This relationship between abundance and node degree
was corroborated by the Spearman's rank correlation coefficient
($r_S = 0.353752$, $p = 6.2933\times10^{-23} $).

>>>>

The degree distribution of this network seems to follow a Poisson distribution
(Pearson’s $\chi^2 = 12.8902$, $\text{p-value} = 0.115684$) characteristic of a
Erdös-Rényi network with many nodes and edges~\cite{Erdos1959}. This kind of
network presents a great
number of nodes with low degree and a few nodes with high degree
(Fig~\ref{fig:deg-dist}A). Nodes corresponding to topologies number one and
three showed the highest degree ($deg(1) = deg (3) = 14$). Curiously, nodes with
higher degree resulted to be also those network topologies with higher abundance
(Fig~\ref{fig:deg-dist}B). This relationship between abundance and node degree
was corroborated by the Spearman's rank correlation coefficient
($r_S = 0.353752$, $p = 6.2933\times10^{-23} $).
